Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-23 tsibbletalk.Rmd
still on linking

There is a three-level hierarchy: the root node is implicitly Australia, and geographically disaggregated to states and lower-level tourism regions. A new handy function `plotly_key_tree()` has been implemented to help explore the hierarchy. It interprets hierarchies in the shared tsibble's `spec` as a tree view, built with \CRANpkg{plotly}. The following code line produces the linked tree diagram (left panel of Figure \ref{fig:tourism-linking-fig}). The visual for the tree hierarchy detangles a group of related series and provides a bird's eye view of the data organisation.

@@

The tree plot provides backbones of the data, and much flesh yet to be attached. Small multiples of time series lines are composed and placed at the top right of Figure \ref{fig:tourism-linking-fig} to unpack the temporal trend across regions by purposes of trips. The shared tsibble data can be directly piped into \CRANpkg{ggplot2} code.

>>>>

\noindent There is a three-level hierarchy: the root node is implicitly Australia, and geographically disaggregated to states and lower-level tourism regions. A new handy function `plotly_key_tree()` has been implemented to help explore the hierarchy. It interprets hierarchies in the shared tsibble's `spec` as a tree view, built with \CRANpkg{plotly}. The following code line produces the linked tree diagram (left panel of Figure \ref{fig:tourism-linking-fig}). The visual for the tree hierarchy detangles a group of related series and provides a bird's eye view of the data organisation.

@@

The tree plot provides the data skeleton, upon which the rest of data can be attached. In this example, small multiples of line plots are placed at the top right of Figure \ref{fig:tourism-linking-fig} to explore the temporal trend across regions, by trip purpose. The shared tsibble data can be directly piped into \CRANpkg{ggplot2} code as follows:

### 2020-09-23 tsibbletalk.tex
still on linking

There is a three-level hierarchy: the root node is implicitly Australia,
and geographically disaggregated to states and lower-level tourism
regions. A new handy function \texttt{plotly\_key\_tree()} has been
implemented to help explore the hierarchy. It interprets hierarchies in
the shared tsibble's \texttt{spec} as a tree view, built with
\CRANpkg{plotly}. The following code line produces the linked tree
diagram (left panel of Figure \ref{fig:tourism-linking-fig}). The visual
for the tree hierarchy detangles a group of related series and provides
a bird's eye view of the data organisation.

@@

The tree plot provides backbones of the data, and much flesh yet to be
attached. Small multiples of time series lines are composed and placed
at the top right of Figure \ref{fig:tourism-linking-fig} to unpack the
temporal trend across regions by purposes of trips. The shared tsibble
data can be directly piped into \CRANpkg{ggplot2} code.

>>>>

\noindent There is a three-level hierarchy: the root node is implicitly
Australia, and geographically disaggregated to states and lower-level
tourism regions. A new handy function \texttt{plotly\_key\_tree()} has
been implemented to help explore the hierarchy. It interprets
hierarchies in the shared tsibble's \texttt{spec} as a tree view, built
with \CRANpkg{plotly}. The following code line produces the linked tree
diagram (left panel of Figure \ref{fig:tourism-linking-fig}). The visual
for the tree hierarchy detangles a group of related series and provides
a bird's eye view of the data organisation.

@@

The tree plot provides the data skeleton, upon which the rest of data
can be attached. In this example, small multiples of line plots are
placed at the top right of Figure \ref{fig:tourism-linking-fig} to
explore the temporal trend across regions, by trip purpose. The shared
tsibble data can be directly piped into \CRANpkg{ggplot2} code as
follows.
